---
title: "Bigram Markov Model"
author: "Benjamin Sherman"
format:
  html:
    code-fold: false
    code-summary: "Show code"
    code-tools: true 
    embed-resources: true

knitr:
  opts_chunk:        ########## set global options ############
    collapse: true   # keep code from blocks together (if shown)
    message: true    # show messages
    warning: false    # show warnings
    error: false      # show error messages
    comment: ""      # don't show ## with printed output
    dpi: 300         # image resolution (typically 300 for publication)
    fig-width: 6.5   # figure width
    fig-height: 4.0  # figure height
    R.options:    
      digits: 3    # round to three digits

---

#### *View below code to see library loading*
```{r}
#| label: library
#| code-fold: TRUE
#install.packages("remotes")
library(remotes)
library(dplyr)
library(tibble)
library(rlang)
library(ggplot2)
library(jsonlite)
library(purrr)
library(tidyr)
library(stringr)
library(httr)
library(readr)
library(kgrams)
library(knitr)
```

#### *View below code to see function loading*

```{r}
#| code-fold: TRUE
chromatic_scale <- c(
  "C"=0, "C#"=1, "Db"=1,
  "D"=2, "D#"=3, "Eb"=3,
  "E"=4, "F"=5, "F#"=6, "Gb"=6,
  "G"=7, "G#"=8, "Ab"=8,
  "A"=9, "A#"=10, "Bb"=10,
  "B"=11
)

reverse_chromatic <- c("C", "C#", "D", "Eb", "E", "F", "F#", "G", "Ab", "A", "Bb", "B")

major_roman <- c("I", "#I/♭II", "II", "#II/♭III", "III", "IV", "#IV/♭V", "V", "#V/♭VI", "VI", "#VI/♭VII", "VII")
minor_roman <- c("i", "#i/♭II", "ii°", "#ii°/♭III", "III", "iv", "#iv/♭V", "V", "#V/♭VI", "VI", "#VI/♭VII", "vii°")

is_minor_key <- function(key) {
  str_detect(key, "m") & !str_detect(key, "maj")
}

extract_root <- function(chord) {
  matches <- str_match(chord, "^([A-G][b#]?)")
  matches[,2]
}

convert_chord_to_roman <- function(chord, key) {
  chord <- str_trim(chord)
  if (is.na(chord) || chord == "") return("")

  key_root <- extract_root(key)
  if (is.na(key_root) || !(key_root %in% names(chromatic_scale))) return(chord)

  tonic_val <- chromatic_scale[[key_root]]
  minor_mode <- is_minor_key(key)
  roman_labels <- if (minor_mode) minor_roman else major_roman

  romanize <- function(note, quality = "") {
    if (!(note %in% names(chromatic_scale))) return(paste0(note, quality))
    interval <- (chromatic_scale[[note]] - tonic_val) %% 12
    paste0(roman_labels[interval + 1], quality)
  }

  # 1. Slash chords (e.g., C/G)
  if (str_detect(chord, "/")) {
    parts <- str_split(chord, "/")[[1]]
    if (length(parts) != 2) return(chord)
    main <- str_trim(parts[1])
    bass <- str_trim(parts[2])

    main_root <- extract_root(main)
    bass_root <- extract_root(bass)

    if (is.na(main_root) || is.na(bass_root)) return(chord)

    main_qual <- str_remove(main, main_root)
    main_roman <- romanize(main_root, main_qual)
    bass_roman <- romanize(bass_root)

    return(paste0(main_roman, "/", bass_roman))
  }

  # 2. Substitution chords (e.g., Cmaj7(Am7))
  if (str_detect(chord, "\\(")) {
    matches <- str_match(chord, "^([A-G][b#]?[^\\(]*)\\(([^\\)]+)\\)")
    if (any(is.na(matches))) return(chord)

    outer <- str_trim(matches[, 2])
    inner <- str_trim(matches[, 3])

    outer_root <- extract_root(outer)
    inner_root <- extract_root(inner)

    if (is.na(outer_root) || is.na(inner_root)) return(chord)

    outer_qual <- str_remove(outer, outer_root)
    inner_qual <- str_remove(inner, inner_root)

    outer_roman <- romanize(outer_root, outer_qual)
    inner_roman <- romanize(inner_root, inner_qual)

    return(paste0(outer_roman, "(", inner_roman, ")"))
  }

  # 3. Regular chords
  root <- extract_root(chord)
  if (is.na(root)) return(chord)

  qual <- str_remove(chord, root)
  romanize(root, qual)
}
```

```{r, echo=FALSE}
CPWK <- read.csv("CPWK2.csv")
```

#### Bigram Markov Function

In this section, I built a simple generative model using bigrams, which are just pairs of consecutive chords (e.g., I → ii, ii → V). By analyzing every chord progression in the dataset, the function counts how often each chord was followed by another and used those counts to calculate transition probabilities. The `generate_sequence()` function then uses these probabilities to simulate new progressions—starting from a given chord (like "I") and sampling each next chord based on the real-world patterns learned from the data.

```{r}
tokenize_chords <- function(prog) {
  bars <- str_split(prog, "\\|")[[1]]
  chords <- unlist(str_split(bars, ","))
  str_trim(chords[chords != ""])
}

chord_sequences <- CPWK$RomanNumeralProgression %>%
  map(tokenize_chords)

bigrams <- map(chord_sequences, ~ tibble(
  from = head(.x, -1),
  to   = tail(.x, -1)
)) %>% bind_rows()

bigram_counts <- bigrams %>%
  count(from, to, name = "n") %>%
  group_by(from) %>%
  mutate(prob = n / sum(n)) %>%
  ungroup()

generate_sequence <- function(start = "I", max_length = 16) {
  seq <- c(start)
  while (length(seq) < max_length) {
    options <- bigram_counts %>% filter(from == last(seq))
    if (nrow(options) == 0) break
    next_chord <- sample(options$to, size = 1, prob = options$prob)
    seq <- c(seq, next_chord)
  }
  return(seq)
}
```

#### Test Generation

Welp, after countless hours spent on scraped models and functions, I finally built a simple version that works. Let's look at the results!

```{r}
set.seed(42)
for (i in 1:8) {
  cat(sprintf("[%02d] %s\n", i, paste(generate_sequence("I"), collapse = ", ")))
}
```
To quote Dr. Frankenstein, "It's alive! It's alive!" I have a lot of thoughts, but let's focus on the positives:

 - The chord progressions (for the most part) are theoretically sound! For example, `Chord Progression [01]` has a great ending. The VI chord into the IIm7-V7 is a good idea, and the IIm7-V7 is perfectly resolved by restarting the chord progression (i.e. going back to the I chord.) There are highs and lows, but you'll have to trust me when I say that - for the most part - there's some coherence here. At least more than previous models.  
 
 - Basic resolution patterns seem to be followed. One of the most standard examples of that is V chords resolving to the I (which has been referenced both above and multiple times throughout the narrative.) We see this happening multiple times in the above progression, but let's go one step further. I wrote some code below to check the model's probabilistic tendencies for what chord to choose next when met with a V7 chord:

```{r}
get_next_chord_distribution <- function(chord, top_n = 10) {
  dist <- bigram_counts %>%
    filter(from == chord) %>%
    arrange(desc(prob))
  
  if (nrow(dist) == 0) {
    cat(sprintf("No data for chord: '%s'\n", chord))
    return(NULL)
  }
  
  # Use kable to display the top transitions
  knitr::kable(head(dist, top_n), caption = paste("Most Likely Chords Following", chord))
}

get_next_chord_distribution("V7")
```
As shown above, a majority of the time it's resolving to some variant of the I chord (I6, Imaj7, I). V -> I is the expected outcome, so this is a great sanity check for the model which it (kinda) passed. There are still some weird options up here (V7 to 	#IV/♭V7?). That will be addressed in a later update.

#### Coverting Results Back to Standard Chords

I'm almost done here, but there's one step left. Musicians don't play from chord progressions in Roman Numeral form (think back to the *Dinah* example), I only did that so the model would capture the chord function within the progression. I wrote code to convert the examples back into standard chords (in the key of C). Additionally, I added an extra feature in the results, and wrote code to test if the resulting chord progression exists in the dataset (i.e. is the model overfitted.) You can see the result for each sequence, where "Exists in dataset: Yes/No" is written.

```{r}
extract_roman_base <- function(roman_string, key_mode = "major") {
  roman_list <- if (key_mode == "minor") minor_roman else major_roman
  roman_list <- roman_list[order(nchar(roman_list), decreasing = TRUE)]
  match <- roman_list[str_detect(roman_string, fixed(roman_list))]
  if (length(match) == 0) return(NA)
  match[[1]]
}

convert_roman_prog_to_chords <- function(roman_prog, key = "C") {
  bars <- str_split(roman_prog, "\\|")[[1]]
  tonic_val <- chromatic_scale[[extract_root(key)]]
  is_minor <- is_minor_key(key)
  key_mode <- if (is_minor) "minor" else "major"
  roman_labels <- if (is_minor) minor_roman else major_roman

  real_chords <- lapply(bars, function(bar) {
    chords <- str_split(str_trim(bar), ",")[[1]]

    sapply(chords, function(rc) {
      rc <- str_trim(rc)
      if (rc == "") return("")

      # 1. Slash chords (e.g. Imaj7/III)
      if (str_detect(rc, "/") & !str_detect(rc, "\\(")) {
        parts <- str_split(rc, "/")[[1]]
        main <- str_trim(parts[1])
        bass <- str_trim(parts[2])
        main_label <- extract_roman_base(main, key_mode)
        bass_label <- extract_roman_base(bass, key_mode)
        if (is.na(main_label) | is.na(bass_label)) return("NA/NA")
        main_qual <- str_remove(main, fixed(main_label))
        bass_interval <- match(bass_label, roman_labels) - 1
        main_interval <- match(main_label, roman_labels) - 1
        bass_note <- reverse_chromatic[(tonic_val + bass_interval) %% 12 + 1]
        main_note <- reverse_chromatic[(tonic_val + main_interval) %% 12 + 1]
        return(paste0(main_note, main_qual, "/", bass_note))
      }

      # 2. Substitution chords (e.g. Imaj7(ii7))
      if (str_detect(rc, "\\(")) {
        matches <- str_match(rc, "^([^\\(]+)\\(([^\\)]+)\\)")
        if (any(is.na(matches))) return("NA/NA")
        outer <- str_trim(matches[,2])
        inner <- str_trim(matches[,3])
        outer_label <- extract_roman_base(outer, key_mode)
        inner_label <- extract_roman_base(inner, key_mode)
        if (is.na(outer_label) | is.na(inner_label)) return("NA/NA")
        outer_qual <- str_remove(outer, fixed(outer_label))
        inner_qual <- str_remove(inner, fixed(inner_label))
        outer_interval <- match(outer_label, roman_labels) - 1
        inner_interval <- match(inner_label, roman_labels) - 1
        outer_note <- reverse_chromatic[(tonic_val + outer_interval) %% 12 + 1]
        inner_note <- reverse_chromatic[(tonic_val + inner_interval) %% 12 + 1]
        return(paste0(outer_note, outer_qual, "(", inner_note, inner_qual, ")"))
      }

      # 3. Regular chord
      roman_label <- extract_roman_base(rc, key_mode)
      if (is.na(roman_label)) return("NA/NA")
      qual <- str_remove(rc, fixed(roman_label))
      interval <- match(roman_label, roman_labels) - 1
      note <- reverse_chromatic[(tonic_val + interval) %% 12 + 1]
      paste0(note, qual)
    })
  })

  paste(sapply(real_chords, function(x) paste(x, collapse = ",")), collapse = " | ")
}

set.seed(45)
for (i in 1:10) {
  roman_seq <- generate_sequence(start = "I", max_length = 8)
  roman_str <- paste(roman_seq, collapse = " | ")
  exists <- roman_str %in% CPWK$RomanNumeralProgression
  cat(sprintf("=== Sequence %02d ===\n", i))
  cat("Roman Numerals:\n", roman_str, "\n")
  cat("Exists in dataset:", ifelse(exists, "Yes", "No"), "\n")
  cat("In C:\n", convert_roman_prog_to_chords(roman_str, key = "C"), "\n\n")
}
```

It's simple and imperfect, but it's functional. If you knew how many days I sunk into models that didn't work, you'd understand why I'm so happy with this result. A great starting point! (Also, the model isn't overfitted re: each progression does *not* exist in the dataset.) 

*P.S. let's ignore the fact that the last chord progression starts with four bars of the "C" chord. Yikes. That'll get fixed later on.*

