---
title: "Logistic Regression"
---


## Model Overview

Logistic regression is used when the dependent variable is binary (0/1, Yes/No, True/False). The model estimates the probability of the dependent variable being 1 given the independent variables.

## Implementation

```{r}
#| label: setup
#| output: false
library(yardstick)
library(tidymodels)
library(tidyverse)
library(here)

```


## Load the data

```{r}
#| label: load-data

analysis_data <- readRDS(here("models", "data", "analysis_data.rds"))
analysis_train <- readRDS(here("models", "data", "analysis_train.rds"))
analysis_test <- readRDS(here("models", "data", "analysis_test.rds"))
analysis_folds <- readRDS(here("models", "data", "analysis_folds.rds"))

```
  
## Recipe
Before fitting the model, I preprocessed the data using a recipe that:

 - Imputes missing values in categorical variables using the mode

 - Imputes missing values in numeric variables using the mean

 - Removes predictors with zero variance

 - Removes highly correlated numeric predictors (correlation threshold = 0.7)

 - Creates dummy variables for categorical predictors
```{r}
#| label: model-rec

weapon_carry_recipe <- 
  recipe(formula = WeaponCarryingSchool ~ ., data = analysis_data) |>
  step_impute_mode(all_nominal_predictors()) |>
  step_impute_mean(all_numeric_predictors()) |>
  step_zv(all_predictors()) |> 
  step_corr(all_numeric_predictors(), threshold = 0.7) 
```

## Bake 
Now, I applied this trained recipe to the data (hence "bake".)
```{r}
rec <- weapon_carry_recipe %>% 
  prep() %>% 
  bake(new_data = analysis_data) %>% glimpse()
```


## Model Specification
Next, I created the framework for a legistic regression that predicts the weapon-carrying variable.  
```{r}
#| label: model-spec

weapon_carry_spec <- 
  logistic_reg() %>% 
  set_mode("classification") %>% 
  set_engine("glm") 

weapon_carry_spec
```

## Workflow  

Combining the above parts, I got the final workflow.  

```{r}
#| label: model-workflow

weapon_carry_workflow <- workflow() %>%
  add_recipe(weapon_carry_recipe) %>%
  add_model(weapon_carry_spec)


weapon_carry_workflow

```

## Application  

Applied to the data, a trained logistic regression model was produced.  

```{r}
#| label: model-fit
mod_1 <- 
  fit(weapon_carry_workflow, data = analysis_train) 

mod_1

```

```{r}
#| label: tidy-model

tidy_model <- 
  mod_1 |>
  tidy(exponentiate = TRUE,
       conf.int = TRUE, 
       conf.level = .95) |>
  mutate(p.value = scales::pvalue(p.value))

tidy_model

```

## A Glimpse At The Resulting Formula

$$
\begin{align*}
\text{logit}(P) =\ & -3.2994 + 0.7495 \cdot \text{AttackedInNeighborhood}_1 + 0.4841 \cdot \text{Bullying}_1 \\
&+ 0.4654 \cdot \text{SexualAbuseByOlderPerson}_1 + 0.7171 \cdot \text{ParentalPhysicalAbuse}_1 \\
&- 0.1592 \cdot \text{ParentSubstanceUse}_1 + \ldots
\end{align*}
$$




## Model Evaluation
Now that the model was created, I tested the predictions with actual data to understand its efficacy.
```{r}
weapon_pred <- 
  augment(mod_1, analysis_train) |> 
  select(WeaponCarryingSchool, .pred_class, .pred_1, .pred_0)

weapon_pred
```
Well, I can't go through the entire list, so I used a confusion matrix to summarize the predictive results of the model.

```{r}
conf_mat_result <- weapon_pred %>%
  conf_mat(truth = WeaponCarryingSchool, estimate = .pred_class)

autoplot(conf_mat_result, type = "heatmap") +
  labs(title = "Confusion Matrix for Weapon-Carrying Model",
       x = "Predicted Class", y = "True Class")
```
It looks like the model has more sensitivity than specificity. I confirmed this by running code to calculate those values.
```{r}
conf_metrics <- summary(conf_mat_result)

conf_metrics %>% 
  filter(.metric %in% c("sens", "spec"))
```

## ROC Plot
Another important tool for understanding predictive power is an ROC plot, which I produced below. The AUC is also printed underneath to quantify the graph’s overall ability to distinguish between students who did and did not carry a weapon.
```{r}
roc_plot_training <- 
  weapon_pred |> 
  roc_curve(truth = WeaponCarryingSchool, .pred_1, event_level = "second") |> 
  autoplot()

roc_plot_training 
```
```{r}
roc_auc_result <- weapon_pred %>%
  roc_auc(truth = WeaponCarryingSchool, .pred_1, event_level = "second")

roc_auc_result
```



## Visualizations
To better interpret the model, the forest plot below highlights the predictive strength and direction of each variable.
```{r}
#| label: visualizations

tidy_model |> 
  filter(term != "(Intercept)") |> 
  ggplot(aes(x = estimate, y = reorder(term, estimate))) +
  geom_point(size = 3) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.2) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "red") +
  scale_x_log10() +
  labs(
    x = "Odds Ratio (log scale)",
    y = "Predictors",
    title = "Forest Plot of Logistic Regression Coefficients"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 10),
    plot.title = element_text(hjust = 0.5)
  )
```


## Results and Interpretation

#### Model Performance
The logistic regression model was successful, but not great. An AUC (area under the curve) of 0.69 is decent for an ROC curve. It was trained to predict weapon-carrying behavior in schools, showing extremely high sensitivity (0.999) but very low specificity (0.014). This indicates that the model is nearly perfect at identifying students who did not carry weapons, but it struggles to correctly identify students who did.

This imbalance suggests the model errs on the side of over-predicting weapon carrying, which may be desirable in some safety-first scenarios (e.g. school interventions), but limits its overall precision.  

This is an example of how simple models (in this case, linear regression) don't always give the intended results, often oversimplifying. Machine learning can be used to increase the precision of our model later on.

#### Predictor Effects  

Still, there are interesting takeaways re: the impact of certain conditions on a teenagers likelihood to bring a gunt o school. In moments like this, we have to remember the story behind the numbers.  

For example, we see variables related to violence massively increase the odds of bringing a gun to school ("AttackedInNeighborhood" and "ParentalPhysicalAbuse" were both in the top three for highest exponentiated logistic regression coefficients.)  

Meanwhile, conditions at school seemed less important ("UnfairDisciplineAtSchool" and "SchoolConnectedness" were the two lowest exponentiated logistic regression coefficients.)
